A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-07-16 博士/论文提交/adversarial_attack/TCSVT/response/response.tex

\begin{table}[h]
    \renewcommand\thetable{X} 
    \centering
    \caption{Untargeted attack: Precision score on OTB2015.}
    \begin{tabular}{@{}ccccc@{}}
    \toprule
    \multirow{2}{*}[-1pt]{Method} & \multirow{2}{*}[-1pt]{Tracker} & \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Attack Cost\\per Frame(ms)\end{tabular}} & \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Before\\ Attack\end{tabular}} & \multirow{2}{*}[-1pt]{Untargeted Attack} \\
        &  &  &  &     \\ \midrule
    RTAA & DaSiamRPN & - & 0.880 & 0.050\\
    SPARK & SiamRPN & 41.4 & 0.851 & 0.064\\
    CSA & SiamRPN & 9 & 0.851 & 0.458\\
    FAN & SiamFC & 10 & 0.720 & 0.180\\
    TTP & SiamRPN++ & 8 & 0.910 & 0.080 \\
    \midrule
    Ours & SiamFC++ & $\sim 0$ & 0.861 & 0.092\\ \bottomrule
    \end{tabular}
    \label{tab:untargeted}
\end{table}

\begin{table}[h]
    \renewcommand\thetable{XI} 
    \centering
    \caption{Targeted attack: Precision score on OTB2015.}
    \begin{tabular}{@{}ccc@{}}
    \toprule
    Method & Tracker &  Targeted Attack \\
    \midrule
    FAN & SiamFC  &0.420 \\
    TTP & SiamRPN++ &0.692 \\
    \midrule
    Ours & SiamFC++  &0.795 \\ \bottomrule
    \end{tabular}
    \label{tab:targeted}
\end{table}

\textbf{
As can be seen from Table \ref{tab:untargeted} and Table \ref{tab:targeted}, CSA reduces the accuracy score with respect to the real trajectory from 0.851 to 0.458. Due to the limitations of the algorithm design, CSA cannot perform targeted attacks for Siamese trackers. Recently, Liang et al. proposed a fast attack network (FAN) \cite{FAN} for attacking SiamFC trackers. To perform untargeted attacks, FAN proposes a drift loss that shifts the tracker's prediction of the target's position. The tracking error accumulates over time until the tracker loses the target completely. To perform targeted attacks, FAN proposes embedding feature loss for improving the similarity between the features of the adversarial sample and the features of regions specified by a particular trajectory. FAN can reduce the accuracy score with respect to the real trajectory from 0.720 to 0.180. However, the accuracy score with respect to fake trajectories is only 0.420. Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information. Nakka et al. \cite{TTP} proposed the temporally transferable perturbations (TTP) for attacking the SiamRPN++ tracker. TTP generates a single adversarial perturbation from the template image and adds this perturbation to each search image of the video. TTP reduces the accuracy score with respect to the real trajectory from 0.910 to 0.080, which is effective for untargeted attacks. However, the accuracy score with respect to the fake trajectory is only 0.692, which demonstrates that TTP's performance of targeted attacks is limited. In addition, this method needs to run a generative network for each video to obtain adversarial information, thus requires the computational and storage resources of the object tracking platform, which makes it difficult to deploy the method to resource-constrained platforms. Our method can reduce the accuracy score with respect to real trajectories from 0.861 to 0.092. The accuracy score is up to 0.795 with respect to fake trajectories, which is significantly better than other methods, and only needs to perform the add operation to generate adversarial information for any video without gradient optimization or network inference.
}

@@

\begin{table}
    \renewcommand\thetable{IX}
    \centering
    \caption{Attack results with or without ground truth (GT) information on GOT-Val.}
    \begin{tabular}{cccc}
        \toprule
        \multirow{2}{*}{Metrics} & \multirow{2}{*}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack}                                            \\
                                 &                                & w/ GT information & w/o GT information \\ \midrule
        SR                       & 0.897                          & 0.123                                & 0.121                                     \\
        AO                       & 0.760                          & 0.153                                & 0.160                                     \\                              
        \bottomrule
    \end{tabular}
    \label{tab:agent}
\end{table}

\textit{3. The technical novelty of this paper is not high as it directly borrows the approach from the traditional adversarial attack and use two additional path to train the neural networks. Can the authors provide theoretical analysis to explain the effectiveness based on such small change?}

% 其他跟踪攻击方法是复杂的，需要设定专门的损失函数和优化方法。我们的攻击方法是简单的，不需要设定专门的损失函数和优化方法。其他攻击方法是非通用的，我们的跟踪方法是通用的。我们之所以能够以简单的方案实现更困难的通用攻击，主要是因为我们放松了对扰动值的限制。如图所示，FAN的SSIM为0.92，我们的扰动的SSIM为0.56。
\textbf{
(1) On one hand, other attack methods on Siamese trackers are complex and require specialized loss functions and optimization methods, while our method is simple and dose not require specialized loss functions and optimization methods.
On the other hand, other attack methods on Siamese trackers are not universal while our method are doubly universal, both with respect to the data and the network architectures.
The main reason why it is possible to implement more difficult universal attacks in a simple scheme is that we relax the constraint on the value of the perturbations, achieving a balance between the attack ability and the perturbation perceptibility.
As shown in Figure \ref{fig:vis}, both FAN \cite{FAN} and our method can perform targeted attack. 
% 添加了由FAN生成的扰动的OTB的SSIM下降至0.92。添加了我们的扰动的OTB的SSIM下降至0.56。
The SSIM of OTB2015 perturbed by FAN drops to 0.92, while the SSIM perturbed by our method drops to 0.56.
By relaxing the constraint on the value of the perturbation, we can achieve better targeted attack performance on OTB2015.
Our method achieves a precision score of 0.795, compared to 0.420 for FAN.
}

\textbf{
(2) To the best of our knowledge, our work is the first attempt to generate video-agnostic perturbations to attack siamese trackers. Besides FGSM \cite{FGSM} and Brown et al.'s work \cite{patch}, other adversarial example generation methods such as C\&W \cite{carlini2017towards} and PGD \cite{PGD} can also be integrated into our attacking system to further improve the attack effect.
In short, we focus on proposing a video-agnostic attacking system for siamese trackers instead of proposing a specific adversarial example generation method.}

\textbf{
(3) By studying the attack method of Siamese trackers, we argue that the disadvantage of Siamese trackers is that template matching-based tracking mechanism is vulnerable to attacks, i.e., if both the template and the search image are perturbed at the same time, then the tracking algorithm can easily be misled.
The implication for improving the tracking robustness is to make the tracker aware of the semantic information of the target being tracked, rather than relying on templates alone.}

### 2021-07-16 博士/论文提交/adversarial_attack/TCSVT/response/response.tex

\newtheorem{example}{Example}
\newtheorem{theorem}{Theorem}

\begin{document}
\setstretch{1.5}
\linespread{1}
\title{Response to Reviewers of TCSVT-06387-2021: A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking}
\author{\normalsize{Zhenbang Li, Yaya Shi, Jin Gao, Shaoru Wang, Bing Li, Pengpeng Liang, Weiming Hu}}
\date{}
\maketitle

\noindent Dear Associate Editor:

We would like to express our heartfelt gratitude to you and the reviewers for the insightful and helpful comments. 
% 指出是主编建议修改后重投的。
The editor-in-chief suggested us to revise the manuscript and resubmit it to TCSVT.
When we revised the paper, we carefully considered and followed all the comments and suggestions provided by you and the reviewers. To summarize, we have made the following revisions:

@@

%%%% 问题 2.1 %%%%
\textit{However, I have some concerns about this paper. 1. Adversarial patch makes the attack very obvious for the human eye. I think the attack should not only for the deep learning model but also for the human eyes.}

\textbf{
% 与模板图像的扰动相同，我们在搜索图像上也牺牲了对抗补丁的一些不可感知性以提高攻击效率。
Thanks for the good comment. Similar to the perturbation on the template image, we sacrifice some imperceptibility of the adversarial patch on the search image to improve the attack efficiency, as shown in Figure \ref{fig:vis}. 
The detailed analysis is added in Section IV.D of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.
}

\begin{figure}[h]
    \renewcommand\thefigure{7}
    \centering
    \subfigure[FAN]{\label{fig:a}\includegraphics[width=0.48\textwidth]{FAN.pdf}}
    \subfigure[Ours]{\label{fig:b}\includegraphics[width=0.48\textwidth]{Ours.pdf}}
    \caption{The results under targeted attacks compared with FAN \cite{FAN}.  FAN crafts the perturbations for each video independently, which comes at a non-negligible computational cost. To achieve video-agnostic universal attack on Siamese trackers, we relax the constraint on the value of the perturbation, achieving a balance between the attack efficiency and the perturbation perceptibility.}
    \label{fig:vis}
\end{figure}

\uline{
% 为了进一步分析扰动的可感知性，我们在图中与FAN进行了对比。
To further analyze the perceptibility of perturbations, we compare our method with FAN \cite{FAN} in Figure \ref{fig:vis}.
% We visualize the perturbed frames ($3^{rd}$ row of Figure \ref{fig:vis}) of OTB2015 dataset, Singer2 video. 
As shown in Figure \ref{fig:vis}, both FAN and our method can perform targeted attack. 
% 添加了由FAN生成的扰动的OTB的SSIM下降至0.92。添加了我们的扰动的OTB的SSIM下降至0.56。
The SSIM of OTB2015 perturbed by FAN drops to 0.92, while the SSIM perturbed by our method drops to 0.56.
% 这是因为FAN为每帧产生独立的扰动，而我们的扰动是通用的，因此我们的任务比FAN更难，导致我们的扰动值更大。
This is because FAN generates independent perturbations for each frame, while our perturbations are universal, which is a more difficult task, resulting in larger values for our perturbations.
By relaxing the constraint on the value of the perturbation, we can achieve better targeted attack performance on OTB2015.
Our method achieves a precision score of 0.795, compared to 0.420 for FAN.
What's more, our method can perform universal attack, both with respect to the data and the network architectures.}

@@

%%%% 问题 2.2 %%%%
\textit{2. Your baseline approaches are not state-of-the-art algorithms. Why not compare to PAT \cite{PAT}, RTAA \cite{RTAA}, SPARK \cite{SPARK} and TTP \cite{TTP}. “However, RTAA only performs the untargeted attacks for trackers, which is less challenging than the targeted attacks in this paper, as we aim to create arbitrary, complex trajectories at test time.” If that is the case, it should be easy to achieve better performance than their approach. I think the experiments should including the methods of untargeted attack.}

\textbf{
Thanks for your advice and we have added experiments as you suggested. We have compared with state-of-the-art attack methods including RTAA, SPARK, TTP, CSA and FAN in both targeted and untargeted attack settings in Section IV. F. Specifically, we have removed the original Table VII included in Section IV.F of the previous manuscript, and added 2 new tables that demonstrate the untargeted and targeted attack results respectively. 
The table demonstrating the untargeted attack result is included in Section IV.F of the revised manuscript and referred to as Table \ref{tab:untargeted}.
The table demonstrating the targeted attack result is included in Section IV.F of the revised manuscript and referred to as Table \ref{tab:targeted}. 
% 我们没有与 PAT 对比，因为他们仅在私有数据上进行了实验，未在公开数据集上进行实验。
We do not compare with PAT because they only experimented on private data and not on the public datasets.
}

@@

\begin{table}[h]
    \renewcommand\thetable{X} 
    \centering
    \caption{Untargeted attack: Precision score on OTB2015.}
    \begin{tabular}{@{}ccccc@{}}
    \toprule
    \multirow{2}{*}[-1pt]{Method} & \multirow{2}{*}[-1pt]{Tracker} & \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Attack Cost\\per Frame(ms)\end{tabular}} & \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Before\\ Attack\end{tabular}} & \multirow{2}{*}[-1pt]{Untargeted Attack} \\
        &  &  &  &     \\ \midrule
    RTAA & DaSiamRPN & - & 0.880 & 0.050\\
    SPARK & SiamRPN & 41.4 & 0.851 & 0.064\\
    CSA & SiamRPN & 9 & 0.851 & 0.458\\
    FAN & SiamFC & 10 & 0.720 & 0.180\\
    TTP & SiamRPN++ & 8 & 0.910 & 0.080 \\
    \midrule
    Ours & SiamFC++ & $\sim 0$ & 0.861 & 0.092\\ \bottomrule
    \end{tabular}
    \label{tab:untargeted}
\end{table}

\begin{table}[h]
    \renewcommand\thetable{XI} 
    \centering
    \caption{Targeted attack: Precision score on OTB2015.}
    \begin{tabular}{@{}ccc@{}}
    \toprule
    Method & Tracker &  Targeted Attack \\
    \midrule
    FAN & SiamFC  &0.420 \\
    TTP & SiamRPN++ &0.692 \\
    \midrule
    Ours & SiamFC++  &0.795 \\ \bottomrule
    \end{tabular}
    \label{tab:targeted}
\end{table}

\textbf{
As can be seen from Table \ref{tab:untargeted} and Table \ref{tab:targeted}, CSA reduces the accuracy score with respect to the real trajectory from 0.851 to 0.458. Due to the limitations of the algorithm design, CSA cannot perform targeted attacks for Siamese trackers. 
SPARK \cite{SPARK} reduces the accuracy score with respect to the real trajectory from 0.851 to 0.064. However, SPARK needs to generate distinct adversarial examples for every search image through heavy iterative schemes, which is time-consuming to attack online-tracking in real time.
RTAA \cite{RTAA} reduces the accuracy score with respect to the real trajectory from 0.880 to 0.050. However, RTAA only performs the untargeted attacks for trackers, which is less challenging than the targeted attacks in this paper, as we aim to create arbitrary, complex trajectories at test time. 
Recently, Liang et al. proposed a fast attack network (FAN) \cite{FAN} for attacking SiamFC trackers. To perform untargeted attacks, FAN proposes a drift loss that shifts the tracker's prediction of the target's position. The tracking error accumulates over time until the tracker loses the target completely. To perform targeted attacks, FAN proposes embedding feature loss for improving the similarity between the features of the adversarial sample and the features of regions specified by a particular trajectory. FAN can reduce the accuracy score with respect to the real trajectory from 0.720 to 0.180. However, the accuracy score with respect to fake trajectories is only 0.420. Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information. 
Nakka et al. \cite{TTP} proposed the temporally transferable perturbations (TTP) for attacking the SiamRPN++ tracker. TTP generates a single adversarial perturbation from the template image and adds this perturbation to each search image of the video. TTP reduces the accuracy score with respect to the real trajectory from 0.910 to 0.080, which is effective for untargeted attacks. However, the accuracy score with respect to the fake trajectory is only 0.692, which demonstrates that TTP's performance of targeted attacks is limited. In addition, this method needs to run a generative network for each video to obtain adversarial information, thus requires the computational and storage resources of the object tracking platform, which makes it difficult to deploy the method to resource-constrained platforms. Our method can reduce the accuracy score with respect to real trajectories from 0.861 to 0.092. The accuracy score is up to 0.795 with respect to fake trajectories, which is significantly better than other methods, and only needs to perform the add operation to generate adversarial information for any video without gradient optimization or network inference.
}

@@

\textbf{
(2) To the best of our knowledge, our work is the first attempt to generate video-agnostic perturbations to attack siamese trackers. Besides FGSM \cite{FGSM} and Brown et al.'s work \cite{patch}, other adversarial example generation methods such as C\&W \cite{carlini2017towards} and PGD \cite{PGD} can also be integrated into our attacking system to further improve the attack effect.
In short, we focus on proposing a video-agnostic attacking system for siamese trackers instead of proposing a specific adversarial example generation method.}

\textbf{
(3) By studying the attack method of Siamese trackers, we argue that the disadvantage of Siamese trackers is that template matching-based tracking mechanism is vulnerable to attacks, i.e., if both the template and the search image are perturbed at the same time, then the tracking algorithm can easily be misled.
The implication for improving the tracking robustness is to make the tracker aware of the semantic information of the target being tracked, rather than relying on templates alone.}

\textit{4. I suggest the authors to add the table to summarize the characteristics of the used datasets.}

\textbf{Thanks for the insightful comment. As suggested, we have added a new table to summarize the characteristics of the used datasets.
The new table is included in Section IV.A of the revised manuscript and referred as Table \ref{tab:dataset}.}

@@

\textit{5. The paper contains some grammar mistakes and typos, the authors need to improve it by double check.}

\textbf{
Thanks for the good comment. We have carefully checked through the whole text and corrected the grammar mistakes and typos. 
Specifically, we have replaced ``Our perturbations also generalize well to SiamFC++-ShuffleNet, in despite of the customized components such as pointwise group convolution and channel shuffle operations in ShuffleNet.'' with}
``
\uline{Our perturbations also generalize well to SiamFC++-ShuffleNet, despite the customized components such as pointwise group convolution and channel shuffle operations in ShuffleNet.}
''
\textbf{in Section IV.E of the revised manuscript.}

\textbf{
We have replaced ``SPARK computes incremental perturbations by using information from the past frames to perform targeted attacks to Siamese trackers.'' with}
``
\uline{SPARK computes incremental perturbations by using information from the past frames to perform targeted attacks on Siamese trackers.}
''
\textbf{in Section II.B of the revised manuscript.}

### 2021-07-16 博士/论文提交/adversarial_attack/TCSVT/latex/main.tex
增加两个算法的实验

We compare the attack method proposed in this paper with the latest attack methods, including CSA \cite{CSA}, RTAA \cite{RTAA}, SPARK \cite{SPARK}, FAN \cite{FAN} and TTP \cite{TTP}. We report the untargeted attack result (Table \ref{tab:SOTA}) and the targeted attack result (Table \ref{tab:SOTA1}) on OTB2015. CSA \cite{CSA} is a Siamese tracking attack method called cooling-shrinking attack. CSA can suppress the peak region on the heat map reflecting the target location, which is used to attack the tracker's targeting ability. CSA can also simultaneously force the tracker's predicted bounding box to shrink, which is used to attack the bounding box regression capability of the tracker. However, this method requires running a generative network for each frame to obtain adversarial information, making it difficult to meet the demand for real-time tracking. CSA reduces the accuracy score with respect to the real trajectory from 0.851 to 0.458. Due to the limitations of the algorithm design, CSA cannot perform targeted attacks for Siamese trackers. Recently, Liang et al. proposed a fast attack network (FAN) \cite{FAN} for attacking SiamFC trackers. To perform untargeted attacks, FAN proposes a drift loss that shifts the tracker's prediction of the target's position. The tracking error accumulates over time until the tracker loses the target completely. To perform targeted attacks, FAN proposes embedding feature loss for improving the similarity between the features of the adversarial sample and the features of regions specified by a particular trajectory. FAN can reduce the accuracy score with respect to the real trajectory from 0.720 to 0.180. However, the accuracy score with respect to fake trajectories is only 0.420. Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information. Nakka et al. \cite{TTP} proposed the temporally transferable perturbations (TTP) for attacking the SiamRPN++ tracker. TTP generates a single adversarial perturbation from the template image and adds this perturbation to each search image of the video. TTP reduces the accuracy score with respect to the real trajectory from 0.910 to 0.080, which is effective for untargeted attacks. However, the accuracy score with respect to the fake trajectory is only 0.692, which demonstrates that TTP's performance of targeted attacks is limited. In addition, this method needs to run a generative network for each video to obtain adversarial information, thus requires the computational and storage resources of the object tracking platform, which makes it difficult to deploy the method to resource-constrained platforms. Our method can reduce the accuracy score with respect to real trajectories from 0.861 to 0.092. The accuracy score is up to 0.795 with respect to fake trajectories, which is significantly better than other methods, and only needs to perform the add operation to generate adversarial information for any video without gradient optimization or network inference.

>>>>

We compare the attack method proposed in this paper with the latest attack methods, including CSA \cite{CSA}, RTAA \cite{RTAA}, SPARK \cite{SPARK}, FAN \cite{FAN} and TTP \cite{TTP}. We report the untargeted attack result (Table \ref{tab:SOTA}) and the targeted attack result (Table \ref{tab:SOTA1}) on OTB2015. CSA \cite{CSA} is a Siamese tracking attack method called cooling-shrinking attack. CSA can suppress the peak region on the heat map reflecting the target location, which is used to attack the tracker's targeting ability. CSA can also simultaneously force the tracker's predicted bounding box to shrink, which is used to attack the bounding box regression capability of the tracker. However, this method requires running a generative network for each frame to obtain adversarial information, making it difficult to meet the demand for real-time tracking. CSA reduces the accuracy score with respect to the real trajectory from 0.851 to 0.458. Due to the limitations of the algorithm design, CSA cannot perform targeted attacks for Siamese trackers. 
SPARK \cite{SPARK} reduces the accuracy score with respect to the real trajectory from 0.851 to 0.064. However, SPARK needs to generate distinct adversarial examples for every search image through heavy iterative schemes, which is time-consuming to attack online-tracking in real time.
RTAA \cite{RTAA} reduces the accuracy score with respect to the real trajectory from 0.880 to 0.050. However, RTAA only performs the untargeted attacks for trackers, which is less challenging than the targeted attacks in this paper, as we aim to create arbitrary, complex trajectories at test time. 
Recently, Liang et al. proposed a fast attack network (FAN) \cite{FAN} for attacking SiamFC trackers. To perform untargeted attacks, FAN proposes a drift loss that shifts the tracker's prediction of the target's position. The tracking error accumulates over time until the tracker loses the target completely. To perform targeted attacks, FAN proposes embedding feature loss for improving the similarity between the features of the adversarial sample and the features of regions specified by a particular trajectory. FAN can reduce the accuracy score with respect to the real trajectory from 0.720 to 0.180. However, the accuracy score with respect to fake trajectories is only 0.420. Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information. Nakka et al. \cite{TTP} proposed the temporally transferable perturbations (TTP) for attacking the SiamRPN++ tracker. TTP generates a single adversarial perturbation from the template image and adds this perturbation to each search image of the video. TTP reduces the accuracy score with respect to the real trajectory from 0.910 to 0.080, which is effective for untargeted attacks. However, the accuracy score with respect to the fake trajectory is only 0.692, which demonstrates that TTP's performance of targeted attacks is limited. In addition, this method needs to run a generative network for each video to obtain adversarial information, thus requires the computational and storage resources of the object tracking platform, which makes it difficult to deploy the method to resource-constrained platforms. Our method can reduce the accuracy score with respect to real trajectories from 0.861 to 0.092. The accuracy score is up to 0.795 with respect to fake trajectories, which is significantly better than other methods, and only needs to perform the add operation to generate adversarial information for any video without gradient optimization or network inference.
